Summary of CA Rice Breeding

### 2017-02-15 output/summary.Rnw
Updated to have estimates from just RES

library(rstan)
library(rstanarm)
source("../src/prep_model_data.R")
load("../output/h1_fit.Rda")

@@

<<fig=TRUE, echo=FALSE>>=
yrs <- 1980:2015
pp <- posterior_predict(release_fit, re.form = NA, newdata = data.frame(release_yr = yrs))
pp <-  pp * 1000 + 9000

@@

>>>>

library(rstan)
library(rstanarm)
library(lme4)

source("../src/prep_model_data.R")
load("h1_fit.Rda")

@@

<<fig=TRUE, echo=FALSE>>=
yrs <- 1980:2015
pp <- posterior_predict(release_fit, re.form = NA, newdata = data.frame(release_yr_c = yrs - 2000))
pp <-  pp * 1000 + 9000

@@

\begin{figure}
<<fig=TRUE, fig.width = 8, fig.height = 5, out.width = '80%', echo=FALSE>>=
tars <- c("M202","M206","M209")
par(mfrow = c(1,3),
    mar = c(4,0,2,0),
    oma = c(4,4,0.5,0.5))

invisible(sapply(tars, function(x){
    plot(yield_lb ~ year, data = mod_data[(mod_data$id == x & mod_data$site == "RES"),],
         xlim = c(1995, 2016), ylim = c(6000,12000),
         pch = 16, main = x,
         ylab = "",
         yaxt = "n",
         xlab = "Year")
    if(x == "M202"){
        axis(2)
        mtext(expression("Yield ( lbs acre"^-1~")"), 2, line = 2.25, cex.lab = 0.6)
    }
    abline(lm(yield_lb ~ year, data = mod_data[(mod_data$id == x & mod_data$site == "RES"),]), lty = 2)

}))

@
\caption{The performance of three major cultivars at the RES site over
time.}
\label{fig:res_yrs}
\end{figure}

\begin{figure}

<<fig=TRUE, echo=FALSE>>=
par(mfrow = c(1,3),
    mar = c(4,0,2,0),
    oma = c(4,4,0.5,0.5))

invisible(sapply(tars, function(x){
    plot(yield_lb ~ yrs_in_trial,
         data = mod_data[(mod_data$id == x & mod_data$site == "RES"),],
         xlim = c(-6, 36), ylim = c(6000,12000),
         pch = 16, main = x,
         ylab = "",
         yaxt = "n",
         xlab = "Years after release")
    if(x == "M202"){
        axis(2)
        mtext(expression("Yield ( lbs acre"^-1~")"), 2, line = 2.25, cex.lab = 0.6)
    }
    abline(lm(yield_lb ~ yrs_in_trial,
              data = mod_data[(mod_data$id == x & mod_data$site == "RES"),]), lty = 2)
}))

@
\caption{The performance of three major cultivars at the RES site
  since the year each cultivar was released.}
\label{fig:res_since_release}
\end{figure}
